---
title: "Technical Analysis of Stocks & Trends"
author: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    theme: united
runtime: shiny
---

```{r setup, include=FALSE}
source('Utilities.R')
library(flexdashboard)
library(tidyquant)
library(TTR)
library(quantmod)
library(data.table)
library(dygraphs)
library(plotly)
library(shiny)
## signals to use 
## SMA  (10, 50, 100, 200 averages along with the slope)
## Bollinger Bands
## UP Down Ratio 
```

```{r}

# constituents = c('RUSSELL1000', 'RUSSELL2000', 'RUSSELL3000', 'DOW', 'SP500')
# allindex = lapply(constituents, tq_index)
# 
# allIndex = data.table(rbindlist(allindex))
# allIndex$symbol  = as.character(allIndex$symbol)
# indexConstituents = allIndex[!duplicated(allIndex[,symbol, company])]
# saveRDS(indexConstituents, 'indexConstituents.rds')
indexConstituents = readRDS('indexConstituents.rds')
tickr = sort(indexConstituents$symbol, decreasing = T)
```



```{r, include=F, eval= T}

priceInput <- reactive({
  
  if(is.null(input$Symbol)){
    symb = 'AAPL'
  } else {
    symb = input$Symbol
  }
  priceData = getSymbols(symb,
                         auto.assign = F)
  names(priceData) = c('Open' ,"High","Low","Close","Volume","Adjusted")
  priceData <- round(priceData[complete.cases(priceData),],2)
  
  
})

dataInput <- reactive({
  
  priceHist = priceInput()
  closePrice = priceHist[,6]
  volume = priceHist[,5]
  
  dr = round(dailyReturn(closePrice)*100,2)
  
  monthRet  =  as.numeric(tail(round(monthlyReturn(closePrice)*100,2),1))
  weeklyRet = as.numeric( tail(round(weeklyReturn(closePrice)*100,2),1))
  dailyRet  = as.numeric( tail(dr,1))
  closingPrice = as.numeric(round(tail(closePrice,1),2))
  
  ## Technical Analysis 
  ma50 = as.numeric(round(tail(SMA(closePrice, n = 50),1),2))
  ma200 = as.numeric(round(tail(SMA(closePrice, n = 200),1)))
  
  ##updownind
  priceHist$posnegCount = ifelse(dr > 0 , 1, -1)
  temp = data.frame(tail(priceHist, 30))
  temp = temp %>% group_by(posnegCount) %>% 
    summarise(TotalVol = sum(Volume, na.rm = T)) %>% arrange(TotalVol)
  upDownRatio = temp$TotalVol[1] / temp$TotalVol[2]
  
  ## RSI 
  RSI =  round(as.numeric(tail(TTR::RSI(price = closePrice,n = 14),1)),2)
  sd_10_30 = tail(TTR::runSD(closePrice, 10),1)/tail(TTR::runSD(closePrice, 30),1)
  vol_10_30 = mean(tail(volume, 10))/mean(tail(volume, 30))
  high_52week = max(tail(closePrice, 252))
  low_52week = min(tail(closePrice, 252))
  
  techlist = list(monthRet = monthRet,
                  weeklyRet= weeklyRet,
                  dailyRet= dailyRet,
                  closingPrice = closingPrice,
                  ma50 = ma50,
                  ma200 = ma200,
                  upDownVolRatio_30D = upDownRatio,
                  rsi = RSI,
                  DailyRet = dr,
                  SD_10_30 = sd_10_30,
                  vol_10_30 = vol_10_30,
                  high_52week = high_52week,
                  low_52week = low_52week)
  
  techlist
})

```

Sidebar {.sidebar}
=====================================

```{r}
selectInput("Symbol", label = "Symbol",
            choices = tickr)
```
This dashboard contains list of stocks in  R3000 + DOW + SP500.
It is designed for traders to get insights about key technical indicators and assist them in trading. 
It can also help investors find an entry point for stocks to open their positions for investments.

__Note__

* If the __closing price > moving averages__, the boxes will be green , otherwise red. 
* If the updown vol ratio is __above 1__, the boxes will be green , otherwise red.



Return History
=======================================================================

Column
-----------------------------------------------------------------------

### Overview
```{r}
renderTable({
  
  stockInfo = (indexConstituents %>% filter(symbol == input$Symbol) %>% 
                 select( - weight,- shares_held))[1,]
  stockInfo = cbind.data.frame(stockInfo,
                               High_52_Week = paste0("$",dataInput()$high_52week),
                               High_52_Week = paste0("$",dataInput()$low_52week))
  
  stockInfo =  as.data.frame( t(stockInfo))
  colnames(stockInfo) = 'Value'
  stockInfo$Info = c( "Symbol",
                      "Company",
                      "Sector",
                      "52 Week High",
                      "52 Week Low")
  
  stockInfo[,c('Info','Value')]
  
})
```



Column
-----------------------------------------------------------------------

### ChartSeries {data-height=900}

```{r}
renderDygraph({
  dygraph(priceInput()[,c('Adjusted','Volume')]) %>%
    dySeries('Volume', color ='red', stepPlot = T, fillGraph = T) %>%
    dySeries('Adjusted', color ='blue',axis = 'y2', drawPoints = T, strokeWidth = 1.5, label = 'AdjustedClose') %>%
    dyRangeSelector(dateWindow = c("2018-01-01", as.character(Sys.Date())))
  
  
})

# renderPlotly({
#   ChartSeriesPlotly(Date = index(priceInput()),
#                     series1 = priceInput()[,5], 
#                     series2 = priceInput()[,6])
# })
```



Technicals
=======================================================================

Row
-----------------------------------------------------------------------

### 1 day Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$dailyRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```

### Weekly Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$weeklyRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```

### Monthly Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$monthRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```


Row 
-----------------------------------------------------------------------

### RSI Indicator

```{r}

renderValueBox({
  techData = dataInput()
  rate = techData$rsi
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < 30 ,"glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate > 70 ,"danger", "success")
  )
})
```

### 50 Day SMA

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$ma50
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < techData$closingPrice ,
                  "glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate >techData$closingPrice ,"danger", "success")
  )
})
```

### 200 Day SMA

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$ma200
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < techData$closingPrice ,
                  "glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate >techData$closingPrice ,"danger", "success")
  )
})
```



Row 
-----------------------------------------------------------------------
### 30 day UpDwn Vol

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$upDownVolRatio_30D
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

### SD of 10D/30D

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$SD_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

### Avg Vol 10D/30D 

```{r}

renderValueBox({
  techData = dataInput()
  rate = techData$vol_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

