---
title: "Technical Indicators"
author: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    theme: cerulean
runtime: shiny
---

```{r setup, include=FALSE}
source('Utilities.R')
source("ReturnIndicators.R")
source("VolumeIndicators.R")
source("VolatilityIndicators.R")
library(flexdashboard)
library(tidyquant)
library(TTR)
library(quantmod)
library(data.table)
library(dygraphs)
library(plotly)
library(shiny)
```

```{r}

# constituents = c('RUSSELL1000', 'RUSSELL2000', 'RUSSELL3000', 'DOW', 'SP500')
# allindex = lapply(constituents, tq_index)
# 
# allIndex = data.table(rbindlist(allindex))
# allIndex$symbol  = as.character(allIndex$symbol)
# indexConstituents = allIndex[!duplicated(allIndex[,symbol, company])]
# saveRDS(indexConstituents, 'indexConstituents.rds')
indexConstituents = readRDS('indexConstituents.rds')
tickr = sort(indexConstituents$symbol, decreasing = T)
```



```{r, include=F, eval= T}

priceInput <- reactive({
  
  if(is.null(input$Symbol)){
    symb = 'AAPL'
  } else {
    symb = input$Symbol
  }
  priceData = getSymbols(symb,
                         auto.assign = F)
  names(priceData) = c('Open' ,"High","Low","Close","Volume","Adjusted")
  priceData <- round(priceData[complete.cases(priceData),],2)
  
  
})

dataInput <- reactive({
  
  priceHist = priceInput()
  closePrice = priceHist[,6]
  volume = priceHist[,5]
  
  ## Return Averages
  dr  = GetReturnSeries(closePrice,dailyReturn = T, weeklyReturn = F, monthlyReturn = F)$dailyRet
  returnSeries=  GetReturnSeries(closePrice, periods = 1)
  closingPrice = as.numeric(round(tail(closePrice,1),2))
  high_52week = max(tail(closePrice, 252))
  low_52week = min(tail(closePrice, 252))
  
  ## Moving Averages
  ma10 = GetMovingAverages(price = closePrice, n = 10, periods = 1)
  ma50  = GetMovingAverages(price = closePrice, n = 50, periods = 1)
  ma200 = GetMovingAverages(price = closePrice, n = 200, periods = 1)
  
  ##Volume Indicators
  upDownRatio = UpDownVolRatio(retSeries = dr, volume = volume,periods = 30)
  vol_10_30 = GetVolRatios(volume = volume, n1 = 10, n2= 30)
  
  # Trend Indicators
  
  # Volatility Indicators
  atr_10_30 = GetATR(ohlc = priceHist,n = 10, periods = 1)/ GetATR(ohlc = priceHist,n = 30, periods = 1)
  
  ## RSI 
  RSI =  round(as.numeric(tail(TTR::RSI(price = closePrice,n = 14,  maType= 'EMA', wts = volume),1)),2)
  sd_10_30 = tail(TTR::runSD(closePrice, 10),1)/tail(TTR::runSD(closePrice, 30),1)
  
  techlist = list(monthRet = returnSeries$monthRet,
                  weeklyRet= returnSeries$weeklyRet,
                  dailyRet= returnSeries$dailyRet,
                  closingPrice = closingPrice,
                  ma10= ma10,
                  ma50 = ma50,
                  ma200 = ma200,
                  upDownVolRatio_30D = upDownRatio,
                  rsi = RSI,
                  SD_10_30 = sd_10_30,
                  vol_10_30 = vol_10_30,
                  high_52week = high_52week,
                  low_52week = low_52week,
                  atr_10_30 = atr_10_30)
  
  techlist
})

```

Sidebar {.sidebar}
=====================================

```{r}
selectInput("Symbol", label = "Symbol",
            choices = tickr, selected = 'TSLA')
```
This dashboard contains list of stocks in  R3000 + DOW + SP500.
It is designed for traders to get insights about key technical indicators and assist them in trading. 
It can also help investors find an entry point for stocks to open their positions for investments.

__Note__

* If the __closing price > moving averages__, the boxes will be green , otherwise red. 
* If the updown vol ratio is __above 1__, the boxes will be green , otherwise red.



Summary
=======================================================================

Column
-----------------------------------------------------------------------

### 
```{r}
renderTable({
  
  stockInfo = (indexConstituents %>% filter(symbol == input$Symbol) %>% 
                 select( - weight,- shares_held))[1,]
  stockInfo = cbind.data.frame(stockInfo,
                               High_52_Week = paste0("$",dataInput()$high_52week),
                               High_52_Week = paste0("$",dataInput()$low_52week),
                               Closing_price = paste0("$",dataInput()$closingPrice))
  
  stockInfo =  as.data.frame( t(stockInfo))
  colnames(stockInfo) = 'Value'
  stockInfo$Info = c( "Symbol",
                      "Company",
                      "Sector",
                      "52 Week High",
                      "52 Week Low",
                      "Closing Price")
  
  stockInfo[,c('Info','Value')]
  
})
```



Column
-----------------------------------------------------------------------

### ChartSeries {data-height=900}

```{r}
renderDygraph({
  dygraph(priceInput()[,c('Adjusted','Volume')]) %>%
    dySeries('Volume', color ='red', stepPlot = T, fillGraph = T) %>%
    dySeries('Adjusted', color ='blue',axis = 'y2', drawPoints = T, strokeWidth = 1.5, label = 'AdjustedClose') %>%
    dyRangeSelector(dateWindow = c("2018-01-01", as.character(Sys.Date())))
  
  
})

# renderPlotly({
#   ChartSeriesPlotly(Date = index(priceInput()),
#                     series1 = priceInput()[,5], 
#                     series2 = priceInput()[,6])
# })
```



Technicals
=======================================================================

Row
-----------------------------------------------------------------------

### 1 day Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$dailyRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```

### Weekly Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$weeklyRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```

### Monthly Return {.value-box}

```{r}
renderValueBox({
  techData = dataInput()
  rate <- formatC(techData$monthRet, digits = 3, format = "f")
  boxCol = ifelse(rate < 0, "danger" , "success")
  valueBox(
    value = paste(rate," %"),
    icon = ifelse(rate >0 ,"glyphicon glyphicon-ok", "glyphicon glyphicon-remove"),
    color = boxCol
  )
})
```


Row 
-----------------------------------------------------------------------

### 10 Day SMA

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$ma10
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < techData$closingPrice ,
                  "glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate >techData$closingPrice ,"danger", "success")
  )
})
```

### 50 Day SMA

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$ma50
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < techData$closingPrice ,
                  "glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate >techData$closingPrice ,"danger", "success")
  )
})
```

### 200 Day SMA

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$ma200
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < techData$closingPrice ,
                  "glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate >techData$closingPrice ,"danger", "success")
  )
})
```



Row 
-----------------------------------------------------------------------
### 30 day UpDwn Vol

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$upDownVolRatio_30D
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

### SD of 10D/30D

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$SD_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

### Avg Vol 10D/30D 

```{r}

renderValueBox({
  techData = dataInput()
  rate = techData$vol_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

Row 
-----------------------------------------------------------------------
### ATR 10D/30D

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$atr_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```

### SD of 10D/30D

```{r}
renderValueBox({
  techData = dataInput()
  rate = techData$SD_10_30
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate > 1 ,
                  "glyphicon glyphicon-arrow-up", "glyphicon glyphicon-arrow-down" ),
    color = ifelse(rate > 1 ,"success", "danger")
  )
})
```


### RSI Indicator

```{r}

renderValueBox({
  techData = dataInput()
  rate = techData$rsi
  rate <- formatC(rate, digits = 2, format = "f")
  valueBox(
    value = rate,
    icon = ifelse(rate < 30 ,"glyphicon glyphicon-thumbs-up", "glyphicon glyphicon-thumbs-down" ),
    color = ifelse(rate <30  ,"success", "danger")
  )
})
```

